---
title: "STA303: W2 optional activity"
subtitle: "More information on joins"
output: learnr::tutorial
css: "css/learnr_303.css"
runtime: shiny_prerendered
---

## Set up and data

Here are the required libraries and the datasets. Credit to Jenny Bryan and team's https://stat545.com/ for the inspiration for this data!

```{r, echo=FALSE, message=FALSE}
# These are the packages you will need for this activity
packages_needed <- c("tidyverse", "learnr", "knitr")

package.check <- lapply(
  packages_needed,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE, repos = "http://cran.us.r-project.org")
    }
  }
)
```


```{r, message=FALSE}
## Load the libraries

library(palmerpenguins)
library(tidyverse)

## Create the datasets

comic_characters <- tibble(
  name = c("Spider Man", "Batman", "Hellboy", "Poison Ivy", "Iron Man", 
           "Scarlet Witch", "Nightwing", "Harley Quinn", "The Sandman"),
  gender = c("masculine", "masculine", "masculine", "feminine", 
             "masculine", "feminine", "masculine", "feminine", "masculine"),
  publisher = c("Marvel", "DC", "Dark Horse Comics", "DC", "Marvel", 
                "Marvel", "DC", "DC", "DC")
)

publishers <- tibble(
  publisher = c("DC", "Marvel"),
  founded = c(1934, 1939)
)

knitr::kable(comic_characters)
knitr::kable(publishers)

```

## Full joins

* Full joins take all the rows from both datasets, matching where possible and just putting NAs where not. 
* The order you put the datasets in will dictate the order of the columns in the resulting dataset. I.e. if you have `full_join(X, Y)` the columns from `X` will appear first, followed by the columns from `Y`.
* Note also that if you don't specify a variable to join 'by', R will try to join by any variables that have the same names in both datasets. It will write a message to you telling you what it did. I prefer to be explicit, it reduces the risk of matching on things I hadn't realized had the same name, but didn't want to match on.

**Try to predict the output before running each chunk**

```{r full1, exercise = TRUE}
full_join(comic_characters, publishers, by = "publisher")
```

```{r full2, exercise = TRUE}
full_join(publishers, comic_characters)
```

So, in our example, we have all rows represented but an `NA` for date founded for Dark Horse Comics because they weren't in our `publishers` data set. Notice the order of the columns in the two examples and the additional message for the second one, `Joining, by = "publisher"`.

\newpage
## Left joins

* Left joins take all the rows from the 'left' dataset, matching where possible and just putting NAs where not. The left dataset in `full_join(X, Y)` is `X.` If there is a level of the matching variable in `Y`, that isn't in `X`, it will be dropped.

Equivalently, in the below, `X` is the 'left' dataset. The result of both these pieces of code is the same.

```
X %>% 
  full_join(Y)
```

* As well as which rows are kept, the order you put the datasets in will dictate the order of the columns in the resulting dataset. I.e. if you have `full_join(X, Y)` the columns from `X` will appear first, followed by the columns from `Y`.
* As above, if you don't specify a variable to join 'by', R will try to join by any variables that have the same names in both datasets.

**Try to predict the output before running each chunk**

```{r left1, exercise = TRUE}
left_join(comic_characters, publishers, by = "publisher")
```

```{r left2, exercise = TRUE}
left_join(publishers, comic_characters, by = "publisher")
```
So, in our example, in the result of the first join, we end up having have all rows from both datasets represented but an `NA` for date founded for Dark Horse Comics because they weren't in our `publishers` data set.

In the result of our second join, because Dark Horse Comics wasn't in the 'left' dataset, we only have 8 rows (instead of 9) and no mention of Hellboy.

Notice the order of the columns in the two examples, also.

\newpage
## Right joins

* Right joins are like left joins, but they take all the rows from the 'right' dataset, matching where possible and just putting NAs where not. The right dataset in `full_join(X, Y)` is `Y`. If there is a level of the matching variable in `X`, that isn't in `Y`, it will be dropped.

Equivalently, in the below, `Y` is the 'right' dataset. The result of both these pieces of code is the same.

```
X %>% 
  full_join(Y)
```

* As well as which rows are kept, the order you put the datasets in will dictate the order of the columns in the resulting dataset. I.e. if you have `full_join(X, Y)` the columns from `Y` will appear first, followed by the columns from `X`.
* As above, if you don't specify a variable to join 'by', R will try to join by any variables that have the same names in both datasets.

**Try to predict the output before running each chunk**

```{r right1, exercise = TRUE}
right_join(comic_characters, publishers, by = "publisher")
```

```{r right2, exercise = TRUE}
right_join(publishers, comic_characters, by = "publisher")
```
So, in the result of our first join, because Dark Horse Comics wasn't in the 'right' dataset, we only have 8 rows (instead of 9) and no mention of Hellboy.

In our second join, we end up having have all rows from both datasets represented but an `NA` for date founded for Dark Horse Comics because they weren't in our `publishers` data set.

Notice the order of the columns in the two examples, also.

